### 2019-05-09 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
I'm happy about the modifications for Chapter 5:
- no proof for lower-bound
- less figures
- shorter Appendix
- few more details in a proof
- less clutter in some equations

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\subsection{Lower bound: proof of Theorem~\ref{thm:5:BetterLowerBound}}
\label{proof:5:BetterLowerBound}

The lower bound that we present relies on the following \emph{change-of-distribution} lemma that we prove in the next section, following recent arguments from \cite{Garivier16TrueShape} that have to be adapted to incorporate the collision information.

\begin{lemma}\label{lem:5:CD} Under observation model \modelun{} and \modeldeux, for every event $A$ that is $\cF_{T}^{j}$-measurable, considering two multi-player bandit models denoted by $\bm{\mu}$ and $\bm{\lambda}$ respectively, it holds that
\begin{equation}
  \sum_{k=1}^{K}\E_{\bm{\mu}}\left[T_k^j(T)\right]\kl(\mu_k,\lambda_k) \geq \kl \left(\Pr_{\bm{\mu}}(A),\Pr_{\bm{\lambda}}(A)\right).
\end{equation}
\end{lemma}

Let $k$ be a sub-optimal arm under $\bm{\mu}$,
fix $\varepsilon \in \left(0, \mu_{M-1}^* - \mu_M^*\right)$,
% We define the bandit instance $\bm{\lambda}$ such that
and let $\bm{\lambda}$ be the bandit instance such that
\[\left\{\begin{array}{ccl}
          \lambda_\ell & = & \mu_\ell \ \ \  \text{for all } \ell \neq k, \\
          \lambda_k & = & \mu_{M^*} + \varepsilon.
         \end{array}
\right.\]
Clearly, $\bm{\lambda}\in\cP_M$ also,
and the set of $M$ best arms under $\bm{\mu}$ and $\bm{\lambda}$ differ by one arm: if \Mbest$_{\bm{\mu}} = \{1^*,\dots,M^*\}$ then $\Mbest_{\bm{\lambda}} = \{1^*,\dots,(M-1)^*,k\}$.
Thus, one expects the ($\cF^j_T$-mesurable) event
\[A_T = \left(T_k^j(T) > \frac{T}{2M}\right)\]
to have a small probability under $\bm{\mu}$ (under which $k$ is sub-optimal) and a large probability under $\bm{\lambda}$ (under which $k$ is one of the optimal arms, and is likely to be drawn a lot).

Applying the inequality in Lemma~\ref{lem:5:CD}, and noting that the sum in the left-hand side reduces to on term as there is a single arm whose distribution is changed, one obtains
\begin{eqnarray*}
  \E_{\bm{\mu}}\left[T_k^j(T)\right] \kl (\mu_k, \mu_{M^*}+\varepsilon) &\geq & \kl \left(\Pr_{\bm{\mu}}(A_T),\Pr_{\bm{\lambda}}(A_T)\right),\nonumber \\
  \E_{\bm{\mu}}\left[T_k^j(T)\right] \kl (\mu_k, \mu_{M^*}+\varepsilon) &\geq & \left(1 - \Pr_{\bm{\mu}}(A_T)\right) \log \left(\frac{1}{\Pr_{\bm{\lambda}}(\overline{A_T})}\right) - \log(2),
\end{eqnarray*}
using the fact that the binary KL-divergence satisfies $\kl(x,y) = \kl(1-x,1-y)$ as well as the inequality  $\kl(x, y) \geq x \log\left(1/y\right) - \log(2)$, proved by \cite{Garivier16TrueShape}.
Now, using Markov inequality yields
\begin{align*}
  \Pr_{\bm{\mu}}\left(A_T\right)
    & \leq 2M\frac{\E_{\bm{\mu}}\left[T^j_k(T)\right]}{T} =: x_T, \\
  \Pr_{\bm{\lambda}}\left(\overline{A_T}\right)
    & = \Pr_{\bm{\lambda}}\left(\frac{T}{M} - T^j_k(T) > \frac{T}{2M}\right) \leq 2M\frac{\E_{\bm{\lambda}}\left[ \frac{T}{M} - T^j_k(T)\right]}{T} =: \frac{y_T}{T},
\end{align*}
which defines two sequences $x_T$ and $y_T$, such that
\begin{eqnarray}\label{eq:5:CqCD}
  \E_{\bm{\mu}}\left[T_k^j(T)\right] \kl (\mu_k, \mu_{M^*}+\varepsilon) &\geq & \left(1 - x_T\right) \log \left(\frac{T}{y_T}\right) - \log(2).
\end{eqnarray}
The strong uniform efficiency assumption (see Definition~\ref{def:5:DecentralizedUniformEfficiency}) further tells us that $x_T \rightarrow 0$ (as $\E_{\bm{\mu}}[T_k^j(T)] = o(T^\alpha)$ for all $\alpha$) and $y_T = o(T^\alpha)$ when $T \to \infty$, for all $\alpha \in (0,1)$.
As a consequence, observe that $\log(y_T)/\log(T) \rightarrow 0$ when $T$ tends to infinity and
\[
  \frac{\left(1 - x_T\right) \log \left({T}/{y_T}\right) - \log(2)}{\log(T)} = 1-x_T - (1-x_T) \frac{\log(y_T)}{\log(T)} - \frac{\log(2)}{\log(T)}
\]
tends to one when $T$ tends to infinity.
From Equation~\eqref{eq:5:CqCD}, this yields
\begin{equation}\label{eq:5:CqCD2}
  \liminf_{T\to\infty} \frac{\E_{\bm{\mu}}[T_k^j(T)]}{\log(T)} \geq \frac{1}{\kl(\mu_k,\mu_{M^*}+\varepsilon)},
\end{equation}
for all $\varepsilon \in \left(0, \mu_{M-1}^* - \mu_M^*\right)$.
Letting $\varepsilon$ go to zero gives the conclusion (as $\kl$ is continuous).

% -----------------------------------------------------------------

\subsubsection{Proof of Lemma~\ref{lem:5:CD}}

Under observation model \modelun{} and \modeldeux, the strategy $A^j(t)$ decides which arm to play based on the information contained in $\cO_{t-1}$, where $\cO_0 = U_0$ and
\[\forall t > 0, \ \ \cO_t = (U_0,Y_1,C_1,U_1,\dots,Y_t,C_t,U_t)\]
where $Y_{t} := Y_{A^j(t-1),t}$ denotes the sensing information, $C_t := C^j(t)$ denotes the collision information (not always completely exploited under observation model \modeldeux) and $U_t$ denotes some external source of randomness\footnote{For instance, \MCTopM, \RandTopM{} and \rhoRand{} draws from a uniform variable in $\{1,\dots,M\}$ for new ranks or arms.} useful to select $A^j(t)$.
Formally, one can say that $A^j(t)$ is $\sigma(\cO_{t-1})$ measurable, if $\sigma(\cO_t)$ denotes the sigma-Algebra generated by the observations $\cO_t$, and as $\cF^j(t) \subseteq \sigma(\cO_{t})$, with an equality under observation model \modelun.

Under two bandit models $\bm{\mu}$ and $\bm{\lambda}$, we let $\Pr_{\bm{\mu}}^{\cO_t}$ (resp. $\Pr_{\bm{\lambda}}^{\cO_t}$) be the distribution of the observations under model $\bm{\mu}$ (resp. $\bm{\lambda}$), given a fixed algorithm.
Using the exact same technique as \cite{Garivier16TrueShape}, called the ``contraction of entropy'' principle, one can establish that for any event $A$ that is $\sigma(\cO_t)$-measurable\footnote{In the work of \cite{Garivier16TrueShape}, the statement is more general and the probability of an event $A$ is replaced by the expectation of any $\cF_T$-measurable random variable $Z$ bounded in $[0,1]$.},
\[\KL\left(\Pr_{\bm{\mu}}^{\cO_t},\Pr_{\bm{\lambda}}^{\cO_t}\right) \geq \kl\left(\Pr_{\bm{\mu}}(A),\Pr_{\bm{\lambda}}(A)\right).\]

The next step is to relate the complicated KL-divergence $\KL\left(\Pr_{\bm{\mu}}^{\cO_t},\Pr_{\bm{\lambda}}^{\cO_t}\right)$ to the number of arm selections.
Proceeding similarly as \cite{Garivier16TrueShape}, one can write, using the chain rule for KL-divergence, that
\begin{equation}\label{eq:5:Iterative}\KL\left(\Pr_{\bm{\mu}}^{\cO_{t}},\Pr_{\bm{\lambda}}^{\cO_{t}}\right) =  \KL\left(\Pr_{\bm{\mu}}^{\cO_{t-1}},\Pr_{\bm{\lambda}}^{\cO_{t-1}}\right) + \KL\left(\Pr_{\bm{\mu}}^{Y_{t},C_t,U_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t},C_t,U_t | \cO_{t-1}}\right).\end{equation}
Now observe that conditionally to $\cO_{t-1}$, $U_t$, $Y_t$ and $C_t$ are independent, as once the selected arm is known, the value of the sensing $Y_t$ does not influence the other players selecting that arm, and $U_t$ is some exogenous randomness.
Using further that the distribution of $U_t$ is the same under $\bm{\mu}$ and $\bm{\lambda}$, one obtains
\begin{equation}\KL\left(\Pr_{\bm{\mu}}^{Y_{t},C_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t},C_t | \cO_{t-1}}\right) =
 \KL\left(\Pr_{\bm{\mu}}^{Y_{t}| \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t}| \cO_{t-1}}\right) + \KL\left(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}\right).\label{eq:5:DecKL}
\end{equation}

The first term in \eqref{eq:5:DecKL} can be rewritten using the same argument as \cite{Garivier16TrueShape}, that relies on the fact that conditionally to $\cO_{t-1}$, $Y_t$ is a Bernoulli distribution with mean $\mu_{A^j(t)}$ under the instance $\bm{\mu}$ and $\lambda_{A^j(t)}$ under the instance $\bm{\lambda}$:
\begin{eqnarray*}
\KL\left(\Pr_{\bm{\mu}}^{Y_{t}| \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t}| \cO_{t-1}}\right)  & = & \E_{\bm{\mu}}\left[\E_{\bm{\mu}}\left[ \KL\left(\Pr_{\bm{\mu}}^{Y_{t}| \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t}| \cO_{t-1}}\right) | \cO_{t-1} \right]\right] \\
& = & \E_{\bm{\mu}} \left[\kl \left(\mu_{A^j(t)},\lambda_{A^j(t)}\right)\right] \\
& = & \E_{\bm{\mu}}  \left[\sum_{k=1}^K \indic{(A^j(t)=k)} \kl \left(\mu_{k},\lambda_{k}\right)\right],
\end{eqnarray*}
We now show that second term in \eqref{eq:5:DecKL} is zero:
\begin{eqnarray*}
\KL\left(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}\right)
& = & \E_{\bm{\mu}}\left[\E_{\bm{\mu}}\left[ \KL\left(\Pr_{\bm{\mu}}^{C_t| \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t| \cO_{t-1}}\right) | \cO_{t-1} \right]\right] \\
& = & \E_{\bm{\mu}}\left[\E_{\bm{\mu}}\left[\E_{\bm{\mu}}\left[ \KL\left(\Pr_{\bm{\mu}}^{C_t| \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t| \cO_{t-1}}\right) | \bigcup_{j' \neq j} \cO_{t-1}^{j'}\right]| \cO_{t-1} \right]\right], \\
\end{eqnarray*}
where $\cO_{t-1}^{j'}$ denote the information available to player $j' \neq j$.
\textcolor{red}{By hypothesis}, the ``collision information term'' is assumed to be a $\smallO{\log(T)}$,
and thus $\KL\left(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}\right) = \smallO{\log(T)}$.

Putting things together, we showed that
\[\KL\left(\Pr_{\bm{\mu}}^{\cO_t},\Pr_{\bm{\lambda}}^{\cO_t}\right) = \KL\left(\Pr_{\bm{\mu}}^{\cO_{t-1}},\Pr_{\bm{\lambda}}^{\cO_{t-1}}\right) + \E_{\bm{\mu}}  \left[\sum_{k=1}^K \indic{(A^j(t)=k)} \kl \left(\mu_{k},\lambda_{k}\right)\right] + \smallO{\log(T)}.\]
Iterating this equality and using that $\KL\left(\Pr_{\bm{\mu}}^{\cO_{0}},\Pr_{\bm{\lambda}}^{\cO_{0}}\right)=0$ yields that
\[\sum_{k=1}^{K}\E_{\bm{\mu}}\left[T_k^j(T)\right]\kl(\mu_k,\lambda_k) \geq \kl \left(\Pr_{\bm{\mu}}(A),\Pr_{\bm{\lambda}}(A)\right) + \smallO{\log(T)},\]
for all $A \in \sigma(\cO_T)$, in particular for all $A \in \cF^j_T$.

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
\subsection{Additional figures}
\label{app:5:moreplots}

We include here plots missing from Section~\ref{sec:5:experiments},
and some additional numerical results.

% -----------------------------------------------------------------
\subsubsection{An illustration of the lower bound}
\label{app:5:illustrationLowerBound}

@@

\paragraph{Additional figures for numerical simulations.}

Figures~\ref{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6}
show the regret $R_T(\boldsymbol{\mu}, M, \rho)$
on the same example problem $\boldsymbol{\mu}$, with $K = 9$ arms and respectively $M = 6$, or $9$ players, for \Selfish-\klUCB.
%
It is just a simple way to check that the two lower bounds on the regret indeed appear as valid lower bounds empirically,
and are moreover lower bounds on the count of selections (\ref{eq:5:term1}, displayed in \textcolor{blue}{cyan}).
%
The lower bounds (in black) are $C(\boldsymbol{\mu}, M) \log t$, the dashed line
for the lower bound from \cite{Zhao10}, and the continuous line is our lower bound.
%
These plot show the regret (in red),
% the three lower bounds
% (centralized, \citeauthor{Anandkumar11}'s and our lower bounds, in black),
and the three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3} in the decomposition of the regret.
As explained in Lemma~\ref{lem:5:DecompositionRegret}, term \ref{eq:5:term2} is not always non-negative.
For $M=9$ and \Selfish, \ref{eq:5:term3} is actually larger than the regret,
and term \ref{eq:5:term1} is zero, as well as the lower bounds.

>>>>

% % -----------------------------------------------------------------
% % -----------------------------------------------------------------
% \subsection{Lower bound: proof of Theorem~\ref{thm:5:BetterLowerBound}}
% \label{proof:5:BetterLowerBound}

% The lower bound that we present relies on the following \emph{change-of-distribution} lemma that we prove in the next section, following recent arguments from \cite{Garivier16TrueShape} that have to be adapted to incorporate the collision information.

% \begin{lemma}\label{lem:5:CD} Under observation model \modelun{} and \modeldeux, for every event $A$ that is $\cF_{T}^{j}$-measurable, considering two multi-player bandit models denoted by $\bm{\mu}$ and $\bm{\lambda}$ respectively, it holds that
% \begin{equation}
%   \sum_{k=1}^{K}\E_{\bm{\mu}}\left[T_k^j(T)\right]\kl(\mu_k,\lambda_k) \geq \kl \left(\Pr_{\bm{\mu}}(A),\Pr_{\bm{\lambda}}(A)\right).
% \end{equation}
% \end{lemma}

% Let $k$ be a sub-optimal arm under $\bm{\mu}$,
% fix $\varepsilon \in \left(0, \mu_{M-1}^* - \mu_M^*\right)$,
% % We define the bandit instance $\bm{\lambda}$ such that
% and let $\bm{\lambda}$ be the bandit instance such that
% \[\left\{\begin{array}{ccl}
%           \lambda_\ell & = & \mu_\ell \ \ \  \text{for all } \ell \neq k, \\
%           \lambda_k & = & \mu_{M^*} + \varepsilon.
%          \end{array}
% \right.\]
% Clearly, $\bm{\lambda}\in\cP_M$ also,
% and the set of $M$ best arms under $\bm{\mu}$ and $\bm{\lambda}$ differ by one arm: if \Mbest$_{\bm{\mu}} = \{1^*,\dots,M^*\}$ then $\Mbest_{\bm{\lambda}} = \{1^*,\dots,(M-1)^*,k\}$.
% Thus, one expects the ($\cF^j_T$-mesurable) event
% \[A_T = \left(T_k^j(T) > \frac{T}{2M}\right)\]
% to have a small probability under $\bm{\mu}$ (under which $k$ is sub-optimal) and a large probability under $\bm{\lambda}$ (under which $k$ is one of the optimal arms, and is likely to be drawn a lot).

% Applying the inequality in Lemma~\ref{lem:5:CD}, and noting that the sum in the left-hand side reduces to on term as there is a single arm whose distribution is changed, one obtains
% \begin{eqnarray*}
%   \E_{\bm{\mu}}\left[T_k^j(T)\right] \kl (\mu_k, \mu_{M^*}+\varepsilon) &\geq & \kl \left(\Pr_{\bm{\mu}}(A_T),\Pr_{\bm{\lambda}}(A_T)\right),\nonumber \\
%   \E_{\bm{\mu}}\left[T_k^j(T)\right] \kl (\mu_k, \mu_{M^*}+\varepsilon) &\geq & \left(1 - \Pr_{\bm{\mu}}(A_T)\right) \log \left(\frac{1}{\Pr_{\bm{\lambda}}(\overline{A_T})}\right) - \log(2),
% \end{eqnarray*}
% using the fact that the binary KL-divergence satisfies $\kl(x,y) = \kl(1-x,1-y)$ as well as the inequality  $\kl(x, y) \geq x \log\left(1/y\right) - \log(2)$, proved by \cite{Garivier16TrueShape}.
% Now, using Markov inequality yields
% \begin{align*}
%   \Pr_{\bm{\mu}}\left(A_T\right)
%     & \leq 2M\frac{\E_{\bm{\mu}}\left[T^j_k(T)\right]}{T} =: x_T, \\
%   \Pr_{\bm{\lambda}}\left(\overline{A_T}\right)
%     & = \Pr_{\bm{\lambda}}\left(\frac{T}{M} - T^j_k(T) > \frac{T}{2M}\right) \leq 2M\frac{\E_{\bm{\lambda}}\left[ \frac{T}{M} - T^j_k(T)\right]}{T} =: \frac{y_T}{T},
% \end{align*}
% which defines two sequences $x_T$ and $y_T$, such that
% \begin{eqnarray}\label{eq:5:CqCD}
%   \E_{\bm{\mu}}\left[T_k^j(T)\right] \kl (\mu_k, \mu_{M^*}+\varepsilon) &\geq & \left(1 - x_T\right) \log \left(\frac{T}{y_T}\right) - \log(2).
% \end{eqnarray}
% The strong uniform efficiency assumption (see Definition~\ref{def:5:DecentralizedUniformEfficiency}) further tells us that $x_T \rightarrow 0$ (as $\E_{\bm{\mu}}[T_k^j(T)] = o(T^\alpha)$ for all $\alpha$) and $y_T = o(T^\alpha)$ when $T \to \infty$, for all $\alpha \in (0,1)$.
% As a consequence, observe that $\log(y_T)/\log(T) \rightarrow 0$ when $T$ tends to infinity and
% \[
%   \frac{\left(1 - x_T\right) \log \left({T}/{y_T}\right) - \log(2)}{\log(T)} = 1-x_T - (1-x_T) \frac{\log(y_T)}{\log(T)} - \frac{\log(2)}{\log(T)}
% \]
% tends to one when $T$ tends to infinity.
% From Equation~\eqref{eq:5:CqCD}, this yields
% \begin{equation}\label{eq:5:CqCD2}
%   \liminf_{T\to\infty} \frac{\E_{\bm{\mu}}[T_k^j(T)]}{\log(T)} \geq \frac{1}{\kl(\mu_k,\mu_{M^*}+\varepsilon)},
% \end{equation}
% for all $\varepsilon \in \left(0, \mu_{M-1}^* - \mu_M^*\right)$.
% Letting $\varepsilon$ go to zero gives the conclusion (as $\kl$ is continuous).

% % -----------------------------------------------------------------

% \subsubsection{Proof of Lemma~\ref{lem:5:CD}}

% Under observation model \modelun{} and \modeldeux, the strategy $A^j(t)$ decides which arm to play based on the information contained in $\cO_{t-1}$, where $\cO_0 = U_0$ and
% \[\forall t > 0, \ \ \cO_t = (U_0,Y_1,C_1,U_1,\dots,Y_t,C_t,U_t)\]
% where $Y_{t} := Y_{A^j(t-1),t}$ denotes the sensing information, $C_t := C^j(t)$ denotes the collision information (not always completely exploited under observation model \modeldeux) and $U_t$ denotes some external source of randomness\footnote{For instance, \MCTopM, \RandTopM{} and \rhoRand{} draws from a uniform variable in $\{1,\dots,M\}$ for new ranks or arms.} useful to select $A^j(t)$.
% Formally, one can say that $A^j(t)$ is $\sigma(\cO_{t-1})$ measurable, if $\sigma(\cO_t)$ denotes the sigma-Algebra generated by the observations $\cO_t$, and as $\cF^j(t) \subseteq \sigma(\cO_{t})$, with an equality under observation model \modelun.

% Under two bandit models $\bm{\mu}$ and $\bm{\lambda}$, we let $\Pr_{\bm{\mu}}^{\cO_t}$ (resp. $\Pr_{\bm{\lambda}}^{\cO_t}$) be the distribution of the observations under model $\bm{\mu}$ (resp. $\bm{\lambda}$), given a fixed algorithm.
% Using the exact same technique as \cite{Garivier16TrueShape}, called the ``contraction of entropy'' principle, one can establish that for any event $A$ that is $\sigma(\cO_t)$-measurable\footnote{In the work of \cite{Garivier16TrueShape}, the statement is more general and the probability of an event $A$ is replaced by the expectation of any $\cF_T$-measurable random variable $Z$ bounded in $[0,1]$.},
% \[\KL\left(\Pr_{\bm{\mu}}^{\cO_t},\Pr_{\bm{\lambda}}^{\cO_t}\right) \geq \kl\left(\Pr_{\bm{\mu}}(A),\Pr_{\bm{\lambda}}(A)\right).\]

% The next step is to relate the complicated KL-divergence $\KL\left(\Pr_{\bm{\mu}}^{\cO_t},\Pr_{\bm{\lambda}}^{\cO_t}\right)$ to the number of arm selections.
% Proceeding similarly as \cite{Garivier16TrueShape}, one can write, using the chain rule for KL-divergence, that
% \begin{equation}\label{eq:5:Iterative}\KL\left(\Pr_{\bm{\mu}}^{\cO_{t}},\Pr_{\bm{\lambda}}^{\cO_{t}}\right) =  \KL\left(\Pr_{\bm{\mu}}^{\cO_{t-1}},\Pr_{\bm{\lambda}}^{\cO_{t-1}}\right) + \KL\left(\Pr_{\bm{\mu}}^{Y_{t},C_t,U_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t},C_t,U_t | \cO_{t-1}}\right).\end{equation}
% Now observe that conditionally to $\cO_{t-1}$, $U_t$, $Y_t$ and $C_t$ are independent, as once the selected arm is known, the value of the sensing $Y_t$ does not influence the other players selecting that arm, and $U_t$ is some exogenous randomness.
% Using further that the distribution of $U_t$ is the same under $\bm{\mu}$ and $\bm{\lambda}$, one obtains
% \begin{equation}\KL\left(\Pr_{\bm{\mu}}^{Y_{t},C_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t},C_t | \cO_{t-1}}\right) =
%  \KL\left(\Pr_{\bm{\mu}}^{Y_{t}| \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t}| \cO_{t-1}}\right) + \KL\left(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}\right).\label{eq:5:DecKL}
% \end{equation}

% The first term in \eqref{eq:5:DecKL} can be rewritten using the same argument as \cite{Garivier16TrueShape}, that relies on the fact that conditionally to $\cO_{t-1}$, $Y_t$ is a Bernoulli distribution with mean $\mu_{A^j(t)}$ under the instance $\bm{\mu}$ and $\lambda_{A^j(t)}$ under the instance $\bm{\lambda}$:
% \begin{eqnarray*}
% \KL\left(\Pr_{\bm{\mu}}^{Y_{t}| \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t}| \cO_{t-1}}\right)  & = & \E_{\bm{\mu}}\left[\E_{\bm{\mu}}\left[ \KL\left(\Pr_{\bm{\mu}}^{Y_{t}| \cO_{t-1}},\Pr_{\bm{\lambda}}^{Y_{t}| \cO_{t-1}}\right) | \cO_{t-1} \right]\right] \\
% & = & \E_{\bm{\mu}} \left[\kl \left(\mu_{A^j(t)},\lambda_{A^j(t)}\right)\right] \\
% & = & \E_{\bm{\mu}}  \left[\sum_{k=1}^K \indic{(A^j(t)=k)} \kl \left(\mu_{k},\lambda_{k}\right)\right],
% \end{eqnarray*}
% We now show that second term in \eqref{eq:5:DecKL} is zero:
% \begin{eqnarray*}
% \KL\left(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}\right)
% & = & \E_{\bm{\mu}}\left[\E_{\bm{\mu}}\left[ \KL\left(\Pr_{\bm{\mu}}^{C_t| \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t| \cO_{t-1}}\right) | \cO_{t-1} \right]\right] \\
% & = & \E_{\bm{\mu}}\left[\E_{\bm{\mu}}\left[\E_{\bm{\mu}}\left[ \KL\left(\Pr_{\bm{\mu}}^{C_t| \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t| \cO_{t-1}}\right) | \bigcup_{j' \neq j} \cO_{t-1}^{j'}\right]| \cO_{t-1} \right]\right], \\
% \end{eqnarray*}
% where $\cO_{t-1}^{j'}$ denote the information available to player $j' \neq j$.
% \textcolor{red}{By hypothesis}, the ``collision information term'' is assumed to be a $\smallO{\log(T)}$,
% and thus $\KL\left(\Pr_{\bm{\mu}}^{C_t | \cO_{t-1}},\Pr_{\bm{\lambda}}^{C_t | \cO_{t-1}}\right) = \smallO{\log(T)}$.

% Putting things together, we showed that
% \[\KL\left(\Pr_{\bm{\mu}}^{\cO_t},\Pr_{\bm{\lambda}}^{\cO_t}\right) = \KL\left(\Pr_{\bm{\mu}}^{\cO_{t-1}},\Pr_{\bm{\lambda}}^{\cO_{t-1}}\right) + \E_{\bm{\mu}}  \left[\sum_{k=1}^K \indic{(A^j(t)=k)} \kl \left(\mu_{k},\lambda_{k}\right)\right] + \smallO{\log(T)}.\]
% Iterating this equality and using that $\KL\left(\Pr_{\bm{\mu}}^{\cO_{0}},\Pr_{\bm{\lambda}}^{\cO_{0}}\right)=0$ yields that
% \[\sum_{k=1}^{K}\E_{\bm{\mu}}\left[T_k^j(T)\right]\kl(\mu_k,\lambda_k) \geq \kl \left(\Pr_{\bm{\mu}}(A),\Pr_{\bm{\lambda}}(A)\right) + \smallO{\log(T)},\]
% for all $A \in \sigma(\cO_T)$, in particular for all $A \in \cF^j_T$.

@@

% -----------------------------------------------------------------
% -----------------------------------------------------------------
% \subsection{Additional figures}
\label{app:5:moreplots}

% We include here plots missing from Section~\ref{sec:5:experiments},
% and some additional numerical results.

% -----------------------------------------------------------------
\subsection*{Illustrating the lower bound}
\label{app:5:illustrationLowerBound}

@@

% -----------------------------------------------------------------
\subsection*{Illustrating the regret decomposition}
\label{app:5:illustrationRegretDecomposition}

The Figure~\ref{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6} below
shows the regret $R_T(\boldsymbol{\mu}, M, \rho)$
on the same example problem $\boldsymbol{\mu}$, with $K = 9$ arms and respectively $M = 6$, or $9$ players, for \Selfish-\klUCB.
%
It is just a simple way to check that the two lower bounds on the regret indeed appear as valid lower bounds empirically,
and are moreover lower bounds on the count of selections (\ref{eq:5:term1}, displayed in \textcolor{blue}{cyan}).
%
The lower bounds (in black) are $C(\boldsymbol{\mu}, M) \log t$, the dashed line
for the lower bound from \cite{Zhao10}, and the continuous line is our lower bound.
%
These plot show the regret (in red),
% the three lower bounds
% (centralized, \citeauthor{Anandkumar11}'s and our lower bounds, in black),
and the three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3} in the decomposition of the regret.
As explained in Lemma~\ref{lem:5:DecompositionRegret}, term \ref{eq:5:term2} is not always non-negative.
For $M=9$ and \Selfish, \ref{eq:5:term3} is actually larger than the regret,
and term \ref{eq:5:term1} is zero, as well as the lower bounds.
